Fusing Filters with Integer Linear Programming

### 2014-04-17 2014betterfusionforfilters/section/03-SizeInference.tex
minor cleanup on judgments

\[ binds \vDash constraint : (\tau_{name} \Rightarrow \tau) \]

@@

\infer{\lambda scalars~arrays \to @let @ binds : \forall_{a \in arrays} k_a. C : T}
      { binds \vDash C : T}

@@

\infer{o = @fold@~f~n; binds \vDash C : \tau_o = k_n, T}
      {binds                 \vDash C : T}

@@

\infer{o = @map@_n~f~ns; binds \vDash \forall k_o.\ \bigwedge_{n \in ns}\{k_o = k_n\} \wedge C : \tau_o = k_o, T}
      {binds                   \vDash C : T}

@@

\infer{o = @filter@~f~n; binds \vDash \exists k_o \le k_n.\ C : \tau_o = k_n, T}
      {binds                   \vDash C : T}
Note that for a filter, the size of the output array $k_o$ is some existential that is less than or equal to $k_n$, but the actual loop size of the \emph{combinator} is equal to $k_n$.
This is because, in order to produce the filtered output, all elements of the input $n$ must be considered.

@@

\infer{o = @gather@~i~d; binds \vDash \forall k_o.\ k_o = k_i \wedge C : \tau_o = k_i, T}
      {binds                   \vDash C : T}

@@

\infer{o = @cross@~a~b; binds \vDash \forall k_o.\ k_o = k_a \times k_b \wedge C : \tau_o = k_a \times k_b, T}
      {binds                  \vDash C : T}

@@

\infer{outs = @external@~ins; binds \vDash \exists_{o \in outs} k_o.\ C : \tau_{outs} = @external@, T}
      {binds                        \vDash C : T}

>>>>

\newcommand{\constraint}[3]{#1 \vDash #2 : #3}
\newcommand{\inferC}[2]{
    $$\begin{array}{c}
        \infer{#1}{#2}
    \end{array}$$}
\newcommand{\ruleIC}[3]{
    \inferC
        {\constraint{#1; binds}{#2 C}{#3 ~ T}}
        {\constraint{binds}{C}{T}}}

\[ \constraint{binds}{constraint}{(\tau_{name} \Rightarrow \tau)} \]

@@

\inferC{\constraint{\lambda scalars~arrays \to @let @ binds}{\forall_{a \in arrays} k_a. C}{T}}
       {\constraint{binds}{C}{T}}

@@

\ruleIC{o = @fold@~f~n}{}{\tau_o = k_n, }

@@

\ruleIC{o = @map@_n~f~ns}{\forall k_o.\ \bigwedge_{n \in ns}\{k_o = k_n\} \wedge}{\tau_o = k_o, }

@@

\ruleIC{o = @filter@~f~n}{\exists k_o \le k_n.\ }{\tau_o = k_n, }

Note that for a filter, the size of the output array $k_o$ is some existential that is less than or equal to $k_n$, but the actual loop size of the \emph{combinator} is equal to $k_n$.
This is because, in order to produce the filtered output, all elements of the input $n$ must be considered.

@@

\ruleIC{o = @gather@~i~d}{\forall k_o.\ k_o = k_i \wedge}{\tau_o = k_i, }

@@

\ruleIC{o = @cross@~a~b}{\forall k_o.\ k_o = k_a \times k_b \wedge C}{\tau_o = k_a \times k_b, }

@@

\ruleIC{outs = @external@~ins}{\exists_{o \in outs} k_o.\ }{\tau_{outs} = @external@, }
